District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa

### 2023-08-24 paper/paper.tex
Updates from Overleaf
Change captions

% Surveys Plot (may be moved to supp. figs)
\begin{figure}
    \centering
    % \includegraphics[width=.9\linewidth]{plots/01_survey_table.pdf}
    \includegraphics[width=.9\linewidth]
    {plots/01_survey_table.png}
    \caption{\emph{Household surveys detailing circumcision patterns in SSA. The colour and size of points are determined by the provider and sample size of each respective survey. Triangular points have no information on circumcision type.}}
\end{figure}

@@

% Map Plot
\begin{figure}
    \centering
    % \includegraphics[width=.9\linewidth]
    \includegraphics[width=1\linewidth]
    % {plots/02_map_plot_facet.png}
    {paper/plots/02_map_plot_facet.png}
    \caption{\emph{Estimated percentage of men aged 10-29 years who were circumcised subnationally in 33 SSA countries in 2006 and 2020, as well as the difference in coverage between the two years. Maps show total male circumcision (MC), medical male circumcision (MMC) and traditional male circumcision (TMC), for which the negative change from 2006 to 2020 is shown, respectively. Missing from map: Guinea-Bissau, Equitorial Guinea, Central African Republic and Botswana}}
\end{figure}
\todo{
  - Use divergent colour palette for "% change", and different one for coverage
- Need to position colour bars under corresponding facets, rather than to the side
- Grey out countries with no type (done)
- reevaluate text size
}

@@

% Subnational coverage plot
\begin{figure}
    \centering
    \includegraphics[width=.9\linewidth]
    {plots/03_subnat_plot.png}
    \caption{\emph{District-level median percentage of men aged 10-29 years who were circumcised in 2020 in 33 SSA countries.
    Each point is a district, sized by district population relative to average district size and coloured by the African region their country falls under (Eastern and Southern Africa (ESA) and Western and Central Africa (WCA), respectively).
    Each white dot represents the national median. A vertical dotted line signifies the UNAIDS target of 90\% national MC.}}
\end{figure}

@@

% Geofaceted plot of 2020 coverage by age
\begin{figure}
    \centering
    \includegraphics[width=.9\linewidth]
    {plots/04_geo_age.png}
    \caption{\emph{Projected percentage of men from 0 to 60 years old who were medically circumcised and traditionally circumcised by 2020. The horizontal grey dashed line indicates the 90\% circumcision coverage by 2021 target established by the UNAIDS Fast Track strategy. Purple areas represent countries where circumcision type could not be ascertained from surveys.}}
\end{figure}

@@

% Dumbbell of type-specific cov change 00'-20'
% todo: Rewrite caption
\begin{figure}
    \centering
    \includegraphics[width=.9\linewidth]
    {plots/05_change_00_20.png}
    % \caption{\emph{Absolute difference, in percentage coverage from 2000 to 2020, coloured by sub-Saharan African region. Plots are split by circumcision type. Countries are ordered from north to south, east to west, and the 13 countries below the black horizontal lines are VMMC priority countries.  }}
    \caption{\emph{Absolute change in circumcision coverage between 2000 and 2020 for 15-29 year olds in all 33 sub-Saharan African countries, split by circumcision type. The countries below the horizontal black line are VMMC priority countries}}
\end{figure}

>>>>

% Surveys Plot (may be moved to supp. figs)
\begin{figure}[H]
    \centering
    % \includegraphics[width=.9\linewidth]{plots/01_survey_table.pdf}
    \includegraphics[width=.9\linewidth]
    {plots/01_survey_table.png}
    \caption{\emph{Household surveys detailing circumcision patterns in SSA. The colour and size of points are determined by the provider and sample size of each respective survey. Triangular points have no information on circumcision type. Cent. Af. Rep. = Central African Republic}}
\end{figure}

@@

% Map Plot
\begin{figure}[H]
    \centering
    % \includegraphics[width=.9\linewidth]
    \includegraphics[width=1\linewidth]
    % {plots/02_map_plot_facet.png}
    {paper/plots/02_map_plot_facet.png}
    \caption{\emph{Estimated percentage of men aged 15-29 years who were circumcised sub-nationally in 33 sub-Saharan African countries in 2006 and 2020, as well as the difference in coverage between the two years. Maps show total male circumcision (MC), medical male circumcision (MMC) and traditional male circumcision (TMC), respectively. Countries with no information on circumcision type are grey in the Medical and Traditional plots, while countries with no circumcision estimate are grey in all.}}
\end{figure}

@@

% Subnational coverage plot
\begin{figure}[H]
    \centering
    \includegraphics[width=.9\linewidth]
    {plots/03_subnat_plot.png}
    \caption{\emph{District-level median percentage of men aged 15-29 years who were circumcised in 2020 in 33 SSA countries.
    Each point is a district, sized by district population relative to average district size.
    Each white dot represents the national median. 
    A vertical dotted line signifies the UNAIDS target of 90\% national male circumcision amongst 15-29 year olds. The countries below the horizontal black line are VMMC priority countries. VMMC = Voluntary Medical Male Circumcision.}}
\end{figure}

\todo{
 - Check UNAIDS target for 15-29 year olds, may be 80\%? May want to remove this line altogether?
}

@@

% Geofaceted plot of 2020 coverage by age
\begin{figure}[H]
    \centering
    \includegraphics[width=.9\linewidth]
    {plots/04_geo_age.png}
    \caption{\emph{Projected percentage of men from 0 to 60 years old who were medically circumcised and traditionally circumcised by 2020. The horizontal grey dashed line indicates the 90\% circumcision coverage by 2021 target established by the UNAIDS Fast Track strategy. Purple areas represent countries where circumcision type could not be ascertained from surveys, and so shows total male circumcision. Cent. Af. Rep. = Central African Republic, Eq. Guinea = Equatorial Guinea.}}
\end{figure}

@@

% Dumbbell of type-specific cov change 00'-20'
% todo: Rewrite caption
\begin{figure}[H]
    \centering
    \includegraphics[width=1\linewidth]
    {plots/06_change_00_20.png}
    % \caption{\emph{Absolute difference, in percentage coverage from 2000 to 2020, coloured by sub-Saharan African region. Plots are split by circumcision type. Countries are ordered from north to south, east to west, and the 13 countries below the black horizontal lines are VMMC priority countries.  }}
    \caption{\emph{Circumcision coverage in 2000 and 2020 amongst 15-29 year olds in all 33 sub-Saharan African countries, split by circumcision type. The countries below the horizontal black line are VMMC priority countries.}}
\end{figure}
